\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{parskip}

\definecolor{primary}{HTML}{166534}
\definecolor{secondary}{HTML}{C9A84C}

\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    filecolor=magenta,      
    urlcolor=primary,
}

\title{Golden Oak School\\ Digital Transformation \& Management Portal\\ User Guide \& Complete Documentation}
\author{ScaleXWebSolution}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Executive Summary}
This document outlines the complete digital transformation of the Golden Oak School web platform. We have transitioned the school from a traditional, static online presence to a \textbf{dynamic, high-performance web application}. 

This new platform serves a dual purpose: it provides a stunning, modern experience for prospective parents and students, while simultaneously offering school administrators a powerful, secure back-office dashboard to manage operations, track analytics, and handle communications seamlessly.

\section{Getting Started: Accessing the Admin Portal}
To manage your new website, you will use the secure Admin Dashboard.

\textbf{Admin Login Details:}
\begin{itemize}
    \item \textbf{Login URL:} \href{https://golden-oak-school.vercel.app/adminlogin}{https://golden-oak-school.vercel.app/adminlogin}
    \item \textbf{Email ID:} \texttt{admin@goldenoakschool.in}
    \item \textbf{Password:} \texttt{GOS3255}
\end{itemize}

\textit{Note: Please keep these credentials secure. Once logged in, you can update your password from the Profile section.}

\section{The Problem vs. The Solution}

Before this project, managing a school website often involved significant friction. Here is how the new Golden Oak School platform solves those legacy issues:

\vspace{1em}
\noindent
\begin{tabularx}{\textwidth}{@{} >{\raggedright\arraybackslash}p{0.45\textwidth} >{\raggedright\arraybackslash}X @{}}
\toprule
\textbf{Previous Challenges (The Problem)} & \textbf{The Golden Oak Solution} \\
\midrule
\textbf{Static Content:} Changing a phone number, adding an announcement, or updating a photo required hiring a developer or touching code. & \textbf{Built-in CMS:} Administrators can now update contact details, upload gallery photos, and post live announcements directly from a visual dashboard. \\
\addlinespace
\textbf{Manual Admissions:} Parents had to visit the school or download PDFs to apply, creating a slow paper trail. & \textbf{Digital Admissions Hub:} Parents apply online. Applications stream instantly into a secure Admin table where staff can track and update the status of each applicant. \\
\addlinespace
\textbf{Lost Communications:} Contact forms sent emails that could bounce, go to spam, or get lost in personal inboxes. & \textbf{Centralized Messages:} All contact messages are saved directly to the database and viewable in the dashboard. Nothing is ever lost. \\
\addlinespace
\textbf{Zero Insights:} No easy way to know if marketing efforts are working or if parents are visiting the site. & \textbf{Live Analytics:} The dashboard automatically tracks daily page views, showing exactly how much traffic the website is generating over 7 and 30 days. \\
\bottomrule
\end{tabularx}
\vspace{1em}

\section{Public Website: Page-by-Page Breakdown}

The public-facing website is designed to be visually engaging, mobile-responsive, and optimized for speed.

\subsection{Home Page}
The gateway to the school. Features a premium "Hero" section, quick links for admissions, and dynamic \textbf{Live Announcements} that scroll across the screen (managed by admins). It also includes a floating WhatsApp button so parents can chat with the office instantly.

\subsection{About Us}
Details the history, mission, and vision of Golden Oak School. Highlights the Principal's message and core values to build trust with prospective families.

\subsection{Academics \& Facilities}
These pages outline the curriculum structure from Nursery to Grade 12, teaching methodologies, and the physical infrastructure of the school (e.g., Smart Classrooms, Labs, Sports facilities). 

\subsection{Image Gallery}
A fully dynamic photo gallery. Instead of rigid, hardcoded images, the gallery pulls photos straight from the secure cloud database. As the school hosts new events, admins can upload photos via the dashboard, and they will appear here instantly.

\subsection{Admissions}
A completely digitized admissions process. 
\begin{itemize}
    \item Outlines the step-by-step process and required documents.
    \item Features a secure \textbf{Online Inquiry Form}. Parents fill in their child's details, the grade they are applying for, and their contact information. 
    \item This data is sent directly to the Admin Dashboard—no emails required.
\end{itemize}

\subsection{Contact Us}
Provides the school's dynamic address, phone numbers, and a Google Map embed. Includes a direct "Message Us" form that, like the admissions form, routes safely to the Admin Dashboard.

\section{The Admin Dashboard: Your Digital Back-Office}

Access the secure backend by navigating to your login URL. This portal is protected by industry-standard encryption and Row Level Security (RLS). This section teaches you how to use every feature from zero-to-all.

\subsection{Dashboard Overview}
The moment you log in, you are presented with the heartbeat of your school's online presence:
\begin{itemize}
    \item \textbf{Traffic Chart:} A visual graph showing how many people visited the website each day for the last week.
    \item \textbf{Metric Cards:} Quick counts of your total published Gallery photos, total Admissions Inquiries waiting for review, and Unread Contact Messages.
\end{itemize}

\subsection{Website Manager (CMS)}
You have full control over the public website without needing to code:
\begin{itemize}
    \item \textbf{Site Details:} Update the school's phone number, email, and Google map link. The website updates instantly.
    \item \textbf{Announcements:} Type an urgent message (e.g., "School closed tomorrow due to rain"), click active, and it immediately appears on the homepage.
    \item \textbf{Gallery Uploads:} A simple drag-and-drop interface to add new photos to the public gallery or remove old ones.
\end{itemize}

\subsection{Admission Inquiries Manager}
A dedicated CRM (Customer Relationship Manager) just for admissions. 
\begin{itemize}
    \item View a table of all submitted applications.
    \item Read the parent's message and see the grade they are applying for by clicking "View Msg".
    \item \textbf{Status Tracking:} Change the status of an application from "Pending" to "Contacted", "Admitted", or "Rejected" to keep your team organized.
    \item Search by parent name or phone number.
\end{itemize}

\subsection{Contact Messages}
A clean inbox for all general questions submitted via the Contact page. You can read, review, and delete spam messages easily.

\subsection{Master Controls \& Security}
\begin{itemize}
    \item \textbf{Audit Logger:} See exactly which administrator changed a setting or uploaded a photo, and when.
    \item \textbf{Maintenance Mode (Super Admin):} If you are doing major updates, a Super Admin can flip one switch. The public website will immediately display a "We are undergoing maintenance" screen while your staff can continue working in the Admin Dashboard unaffected.
\end{itemize}

\section{Pricing \& Maintenance}
\begin{itemize}
    \item \textbf{Domain \& Hosting:} If you require a private custom domain (e.g., goldenoakschool.in), standard domain registration and associated hosting charges will apply.
    \item \textbf{Free Maintenance:} We are pleased to offer \textbf{6 months of free maintenance} and technical support to ensure your platform runs flawlessly.
\end{itemize}

\section{About ScaleXWeb Solution}
This digital transformation was architected and developed by \textbf{ScaleXWeb Solution}. We specialize in delivering high-end, dynamic web applications for modern institutions.
\begin{itemize}
    \item \textbf{Agency Website:} \href{https://scalexwebsolution.vercel.app/}{https://scalexwebsolution.vercel.app/}
    \item \textbf{Project Live URL:} \href{https://golden-oak-school.vercel.app/}{https://golden-oak-school.vercel.app/}
\end{itemize}

\section{Conclusion}
The Golden Oak School platform is no longer just a digital brochure; it is an active operational tool. By centralizing content management, digitizing admissions, and providing real-time traffic insights, this platform significantly reduces administrative overhead and provides a premium, seamless experience for your community.

\end{document}